Arbitrary Fault-Tolerant and Locality-Aware MapReduce

### 2019-09-30 Paper.tex
Andrea

\title{Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce}

@@

Another very important aspect of PP is its ability to recognize duplicated requests coming from client (which can retransmitt a same request) re-forwarding responses; in other words, we have adopt a \textit{most-once semantics}. Note that WP too are designed according to most-once semantics.

@@

Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs. If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG.

>>>>

\title{Arbitrary Fault-Tolerant and Locality-Aware MapReduce}

@@

Another very important aspect of PP is its ability to recognize duplicated requests coming from client (which can re-transmit a same request) re-forwarding responses; in other words, we have adopt a \textit{most-once semantics}. Note that WP too are designed according to most-once semantics.

@@

Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs. If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG. te
